Global adjoint tomography -- Model GLAD-M25\footnote{This paper is dedicated to Dimitri Komatitsch, computational geophysicist extraordinaire, who passed away unexpectedly shortly before its submission.}

### 2020-02-17 response_to_reviewers.tex

\rev{The authors describe a global waveform inversion based on spectral-element simulations and adjoint techniques. The outline follows numerous previous publication of roughly the same group of authors: presentation of the initial model, the distribution of events, of data and measurements, model parametrization, workflow, misfit evolution, and the final model.

I am fully aware that such an inversion is technologically challenging, and that the authors aim to publish the current state of their model. However, I have some rather serious and fundamental concerns that I would like to see addressed before making any more detailed comments. Specifically, I have difficulties to discover any true scientific innovation. To me, adding some events and slightly reducing the minimum period is clearly too incremental. If our community were to operate in such a mode, we would see a flood of tomographic models, each being an update of its predecessor with a few more iterations. This would slow down progress instead of accelerating it. Furthermore, the absence of even the slightest effort to assess the resolution of the model is hardly acceptable. Of course, nobody would request that the full resolution operator be computed for such an inversion, but some reasonable effort must be made. Simply writing that you ran out of computational resources to check the quality of the model is rather dubious.

As I wrote before, I perfectly know that this inversion is not a trivial task, and I do believe that it should be published somewhere. However, I really do not think that GJI is a suitable journal for this manuscript. My suggestion would be to refocus the manuscript on the technical and computational aspects, and to send it to a computational science journal.
}

\response{We appreciate the scientific criticisms of the reviewer.
We believe that both technically and scientifically our community will benefit from our efforts and experiences, because this is the first time this volume of data is
assimilated in such a computationally large-scale global inversion.
Therefore,
we believe that GJI is the right journal for this manuscript,
especially in view of the fact that many other papers on earthquake FWI/adjoint tomography have been published in GJI.
We do not agree with the reviewer that the slight reduction in minimum period is too incremental, and should thus not be considered scientific progress.
In fact, even though the period range of GLAD-M25 is similar to that of GLAD-M15,
we observe significant differences between the two models,
thanks to the 10 additional iterations and a 6-fold increase in the number of earthquakes,
including more than 500 deep events with very clean body waves.
Belittling our work with comments like ``adding some events'' when scaling the inversion up from 253 events to 1,480 events involved a herculean effort, especially on behalf of the first-author graduate student, is totally unprofessional and completely uncalled for.

@@

We naively assumed that it was obvious from the GLAD-M15 GJI article and the histograms and comparisons with other models in this manuscript.
However, based on the comments of all the reviewers we now directly compare GLAD-M15 and GLAD-M25 in the revised manuscript,
thereby highlighting visual differences between the models, in addition to the the tables with variance reductions and traveltime and amplitude anomaly histograms.

There is still a vast amount of information to be explained in seismograms at the global scale, which requires more iterations and, probably, a more complete parameterization.
However, the reviewer is missing the main point --- or, more likely, we did not explain it well --- which is that we decided to publish GLAD-M25 because its resolution (scale-length of heterogeneities) has become comparable to the current resolution of global models from various other groups.
Thus we did not arbitrarily decide to publish this model,
and we certainly do not advocate publishing every iteration as a new model.
%We now highlight it in the manuscript that the vast amount of remaining data in the seismograms should continue changing the models which also points out the necessity of our non-linear iterative inversions.

Finally, resolution and uncertainty quantification remain a challenge in FWI,
both in exploration and earthquake seismology.
In lieu of such tools,
as in numerous other studies,
we used traveltime histograms and a held-out dataset to assess performance of our model (thus, it is not a fair comment that even the slightest effort to assess the resolution of the model is absent in the original submission).
In the original submission, we did not perform PSF tests, because these are rather limited in value, especially in view of the fact that they only tell you something about one ``point'' in the model for the set up of a particular iteration.
Therefore, a PSF does not say much about uncertainty, but gives an idea of resolution.
Nevertheless,
as mentioned earlier,
the updated manuscript now contains four PSF tests,
and the SOM contains two more.}

### 2020-02-17 main.tex
Updates from Overleaf

Global adjoint tomography has a well-defined but complex workflow with multiple stages.
% including numerical simulations of synthetic seismograms (forward simulations) for all events,
% pre-processing of seismic data, making measurements, data assimilation, Fr\'echet derivative
% calculations (adjoint simulations), and post-processing of the gradient for quasi-Newton model
% updates.
It is essential to optimize, automate, and harden the entire process using workflow management tools, especially with large data sets.
For each iteration,
1,480 forward and adjoint simulations need to be performed (one pair for each earthquake in the database),
generating a few Petabytes of wavefield files for the parsimonious-storage kernel calculation algorithm of~\cite{KoXiBoPeSaLiTr16}, and consuming 16~million OLCF node hours.

@@

Fig.~\ref{fig:eventsstations}(a) shows a map of the 1,480 earthquakes
selected from the global Centroid-Moment Tensor (CMT) catalog~\citep[e.g.,][]{ekstrom2012global}
and used in this study.
To ensure a good signal-to-noise ratio on a global scale,
the smallest moment magnitude in the database is set to~5.5,
thereby capturing more deep events,
and, to avoid complications associated with source dimension and directivity,
the largest moment magnitude is set to~7.2.
Prior to the structural inversion,
we performed source inversions using model GLAD-M15 and the CMT inversion algorithm of \cite{liu2004spectral},
as described in the Supplementary Online Material (SOM).

@@

The seismographic stations used in this study are plotted in Fig.~\ref{fig:eventsstations}(b) and
were selected to optimize global coverage
and high data quality.
In addition to the seismographic  stations used for the source inversions,
we included available data for our 1,480 event earthquake database from many data centers,
including IRIS, ORFEUS, INGV, IPGP, ETH, and GEONET.
Regional and temporary networks,
such as US Array~(TA),
Africa Array~(AF), the Canadian National Seismograph Network~(CN), Geoscience Australia~(AU),
the Antarctic Seismographic Argentinean Italian Network~(AI),
and the New Zealand National Seismograph Network~(NZ),
constitute a significant part
of our database and greatly improve coverage in certain regions.

@@

The misfit function to be minimized must
be carefully constructed.
In this study,
it involves cross-correlation traveltimes
for body waves and frequency-dependent multitaper phase measurements for surface waves.
Measurements are made in several passbands of three-component seismograms rotated
into vertical, radial, and transverse components, resulting in a number of measurement
categories.
In this study, we consider four passbands, namely, a 17--40~s passband targeting body waves,
two 40--100~s passbands separately targeting body and surface waves,
and a 90--250~s passband targeting longer-period surface waves.
Each passband involves measurements on all three components,
which results in a total of twelve measurement categories.
Although the inversion is designed to minimize the overall misfit,
we track the misfit reduction in each of the categories to ensure that
the model is improving the fit to the data roughly equally.
One of the biggest challenges in the construction of the misfit function is the
highly uneven distribution of earthquakes and seismographic stations,
which must be counterbalanced by geographically weighting the data.
This issue is discussed in detail by~\cite{Ruanetal2018};
in this section we present a brief synopsis.

With these considerations in mind,
the overall misfit, $\Phi$, is defined as follows:
\begin{equation}
\label{eq:misfit}
\Phi = \sum_{s}^{S} \omega_s \sum_{c}^{C} \omega_{c} \sum_{r}^{R_{sc}} \omega_{scr} \sum_{w}^{W_{scr}} \omega_{scrw}\, \chi_{scrw}
\quad .
\end{equation}
Here~$S$ denotes the number of sources, $C$ the number of categories,
$R_{sc}$ the number of receivers recording source~$s$ in category~$c$,
and~$W_{scr}$ the number of measurement windows for source~$s$, category~$c$,
and receiver~$r$.
The misfit for a specific source~$s$, category~$c$, receiver~$r$, and window~$w$ is
\begin{equation}
  \chi_{scrw} = \frac{1}{\Delta\omega}\int_{\omega_1}^{\omega_2} \Big( \frac {\Delta \tau_{scrw}} {\sigma_{scrw}} \Big)^2\, \mathrm{d}\omega
\quad ,
\end{equation}
where~$\Delta \tau_{scrw}$ denotes a multi-taper frequency-dependent phase measurement over the frequency interval~$\Delta\omega=\omega_2-\omega_1$\,,
with associated uncertainties~$\sigma_{scrw}$\,.
For body waves, the window misfit is often simply the cross-correlation traveltime anomaly,
$\Delta T_{scrw}$\,, weighted by its standard deviation, i.e., $\chi_{scrw}=(\Delta T_{scrw}/\sigma_{scrw})^2$\,.
The window weights are all equal, $\omega_{scrw}=1$\,,
and the category weight, $\omega_c$\,, is the reciprocal of the number of measurements in that
category, $1/C$.
Earthquakes mainly occur along plate boundaries,
and most seismographic  stations are confined to the continents,
which leads to an uneven distribution of sources and stations,
as illustrated in Fig.~\ref{fig:eventsstations}.
Therefore, weighting is crucial in global tomography to balance this uneven sampling
of Earth's interior.
Our source and receiver weighting strategy,
encapsulated by the weights~$\omega_s$ and $\omega_{scr}$\,,
is developed to compensate for uneven spatial sampling.
We define source and receiver weights as
\begin{equation}
\omega_{s}^{-1} = N\,\sum_{s'=1}^{S} \exp\left[\mbox{}-\left(\frac{\Delta_{ss'}}{\Delta}\right)^2\right]
\quad ,
\label{eq:source_weights}
\end{equation}
and
\begin{equation}
\omega_{scr}^{-1} = N_{sc}\,\sum_{r'=1}^{R_{sc}} \exp\left[\mbox{}-\left(\frac{\Delta_{rr'}}{\Delta_{sc}}\right)^2\right]
\quad ,
\label{eq:receiver_weights}
\end{equation}
respectively.
Here~$N$ and~$N_{sc}$ are normalization factors,
and~$\Delta_{ss'}$ and~$\Delta_{rr'}$ denote angular distances between source and receiver pairs~$\{s,s'\}$ and~$\{r,r'\}$\,.
The reference angular distances~$\Delta$ and~$\Delta_{sc}$ need to be chosen based on the condition 
numbers of the diagonal weighting matrices defined by Eqns.~(\ref{eq:source_weights}) and~(\ref{eq:receiver_weights}).

@@

In this section we calculate specific changes in misfit using all 1,480
earthquakes and an identical set of weights and windows for three models,
namely, GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
Table~\ref{table:misfit_reduction_M15_M25} summarizes the changes in fit in
the twelve measurement categories between the new model, GLAD-M25, and its
starting model, GLAD-M15, and between GLAD-M25 and model S362ANI combined
with CRUST2.0, which was the starting model for the GLAD-M15 inversion.

@@

Another way to evaluate model quality is by assessing the distribution
of measurements in the various categories.
Again we use all 1,480 events and a set of identical windows on all three components
to assess GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
The total number of selected windows,
determined using model GLAD-M25, exceeds 18~million.
Fig.~\ref{fig:phase_hist} shows histograms of the resulting phase
measurements in all twelve measurement categories.
We observe that the distributions generally become better centered on zero,
and that all standard deviations are steadily reduced.
The inversion is aimed at reducing the overall misfit,
so there are small tradeoffs between different measurement categories.

@@

Fig.~\ref{fig:psf_tests} shows the results of the four PSF tests we performed for model GLAD-M25.
The first test repeats an analysis performed by~\cite{bozdaug2016global} for GLAD-M15 in the upper mantle underneath Yellowstone.
That test was based on 253 earthquakes,
and Figs.~\ref{fig:psf_tests}a shows our result for the same location based on the current dataset of 1,480 events.
We observe that the 100~km diameter anomaly at 300~km depth is well recovered, with little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and~$c$ (See SOM).
Figs.~\ref{fig:psf_tests}b--d shows the results of PSF tests in the lower mantle beneath Afar,
in the lowermost mantle beneath Easter Island,
and in the mid mantle below Sumatra.
In each case the Gaussian anomaly is well recovered, with minimal tradeoff with other model parameters (See SOM).

@@

Following the approach of \cite{tape2009adjoint}, \cite{chen2015multiparameter},
and \cite{bozdaug2016global}, we selected 360 earthquakes that were not used
in the actual inversion. This held-out data set consists of all magnitude 6.3--7.0
earthquakes in the global CMT catalog that were not used in the inversion.
We chose larger events to generate as many measurements as possible.
We calibrated the centroid time and scalar moment using a grid search based on
3D synthetics calculated in GLAD-M25.
Fig.~\ref{fig:events_360} summarizes the properties of the held-out database.

First, we repeated the misfit assessment discussed in
Section~\ref{section:Misfit assessment} for the held-out database.
Table~\ref{table:misfit_reduction_M15_M25_360} summarizes the reductions
in misfit for the held-out database for model GLAD-M25 compared to GLAD-M15
as well a S362ANI combined with CRUST2.0.
It is encouraging to see that the reductions are comparable to the
values tabulated in Table~\ref{table:misfit_reduction_M15_M25} for the actual inversion.
Overall, the reductions are slightly smaller, partly due to the fact that we did not
conduct full CMT inversions for the held-out database.

\begin{table}
  \centering
  %\label{tab:category}
  \begin{tabular}{|c|c|c|c|}
  \hline
  ~          &  Vertical (\%) & Radial (\%) &  Transverse (\%) \\
  \hline
  17--40~s                &          11.8 (29.2) &       14.1 (33.7) &       21.5 (43.4) \\
  40--100~s body waves    &          14.5 (26.2) &       12.9 (32.2)  &       16.9 (39.0) \\
  40--100~s surface waves &          29.3 (49.1) &       28.1 (49.4) &       23.7 (51.2) \\
  90--250~s               &          10.9 (30.9) &       14.3 (34.8)  &       24.0 (34.9) \\
  \hline
  \end{tabular}\\
  \caption{\small{Changes in fit for 360 earthquakes not used in the inversion in the twelve measurement categories
between the new model, GLAD-M25, and its starting model, GLAD-M15, and, in parentheses, between GLAD-M25 and model S362ANI combined with CRUST2.0, which was the starting model for the GLAD-M15 inversion.}}
  \label{table:misfit_reduction_M15_M25_360}
\end{table}

@@

Vertical cross sections are plotted relative to the spherical average of GLAD-M25,
as discussed in Appendix~\ref{sec:1Dmodel}.
For plotting purposes and use in other applications,
an expansion of the model in spherical harmonics and radial B-splines is
discussed in Appendix~\ref{sec:shanalysis}.

@@

Relative to our first generation model GLAD-M15,
we observe a significant increase in model perturbation amplitudes and resolution,
both in the upper and lower mantle.
To illustrate this point,
Fig.~\ref{fig:power} and Fig.~\ref{fig:powerspectraradius} show normalized power per angular degree (Eqn.~\ref{eq:powerdegree}) and normalized power per angular degree as a function of radius (Eqn.~\ref{eq:powerdegreeradius}), respectively, for models S362ANI, GLAD-M15, and GLAD-M25.
Model S362ANI has no power beyond degree~18,
and we see and increase in power for GLAD-M25 relative to GLAD-M15 beyond degree~10 throughout the mantle.

@@

As illustrated in Fig.~\ref{fig:M25-AFAR},
we see an enhancement of the Afar plume relative to GLAD-M15.
The 3D morphology of the African superplume shows a mantle plume rising from the core-mantle boundary with a broad base tilting northward with a thinning neck, before it reaches the 660~km phase boundary and flattens.
It then develops into two sub-plumes ---Afar and East Lake Victoria--- supplying the East Africa rift.
The development of the superplume and its 3D morphology might be associated with water in the mantle transition zone, a possibility we will explore in a future study.

Subduction along the Andes in South America is imaged from south to north all the way down to the transition zone and beyond, as shown in Fig.~\ref{fig:S_America}.
In the contour plot of positive shear-wavespeed perturbations we observe three gaps, which may correspond to ridges or volcanic plateaus on the subducted Nazca plate, and indicate a weakened or even torn slab.

Fig.~\ref{fig:M24-Iceland} showcases the north Atlantic, where we see clear expressions of the Jan Mayen and Iceland plumes as well as the Azores, Canary Islands, and Bermuda,
and Fig.~\ref{fig:M24-Reunion} shows the emergence of hotspots in the Indian Ocean in model GLAD-M25,
including Marion, Crozet, Kerguelen, Cocos, R\'eunion, and Seychelles.

@@

Overall, the three models are in reasonably good agreement.
At shallow depths, model GLAD-M25 shows more distinct continental crust and cratons, thanks to the inclusion of surface waves.
But in the upper and mid mantle,
the models share similar attributes.

@@

Although Figs.~\ref{fig:window_density_Z}--\ref{fig:window_density_T} illustrate that much information in seismograms is
being assimilated, we still have a long way to go before explaining every broadband wiggle in hundreds-of-minutes-long seismograms.
Currently, we are only fitting the phase in selected time windows, and amplitude information remains completely unused.
We accommodate the full physics of seismic wave propagation,
but we are not exploiting the most general earth model parameterization.
GLAD-M25 is an elastic model with radial anisotropy confined to the upper mantle.
It is well known that the upper mantle is azimuthally anisotropic~\citep[e.g.,][]{montagner1989petrological,montagner1991},
and we also know that amplitude information helps constrain second derivatives in phase speed~\citep[e.g.,][]{WW86,TDI,TDII},
in addition to lateral variations in attenuation~\cite[e.g.,][]{romanowicz1998,reidetal2001,DaEkDz08}.
Thus, the natural next step in global FWI is to use phase and amplitude information simultaneously to jointly constrain the elastic and anelastic structure of the Earth.
To accomplish this next step, source parameters need to be constrained more precisely, especially as we push the resolution to shorter periods~\citep[e.g.,][]{valentine2010}.

>>>>

Global adjoint tomography has a well-defined but complex workflow with multiple stages.
% including numerical simulations of synthetic seismograms (forward simulations) for all events,
% pre-processing of seismic data, making measurements, data assimilation, Fr\'echet derivative
% calculations (adjoint simulations), and post-processing of the gradient for quasi-Newton model
% updates.
It is essential to optimize, automate, and harden the entire process using workflow management tools, especially with large data sets.
In this study, for each iteration,
1,480 forward and adjoint simulations need to be performed (one pair for each earthquake in the database),
generating a few Petabytes of wavefield files for the parsimonious-storage kernel calculation algorithm of~\cite{KoXiBoPeSaLiTr16}, and consuming 16~million OLCF node hours (\cyan{on Summit or Titan node hours? I think 1480 was gradually assimilated}).

@@

Fig.~\ref{fig:eventsstations}(a) shows a map of the 1,480 earthquakes
selected from the global Centroid-Moment Tensor (CMT) catalog~\citep[e.g.,][]{ekstrom2012global}
and used in this study.
To ensure a good signal-to-noise ratio on a global scale,
the smallest moment magnitude in the database is set to~5.5 \cyan{5.5 is already the minimum period in globalcmt. Is it really the minimum? },
thereby capturing more deep events,
and, to avoid complications associated with source dimension and directivity,
the largest moment magnitude is set to~7.2.
Prior to the structural inversion,
we performed source inversions using model GLAD-M15 and the CMT inversion algorithm of \cite{liu2004spectral},
as described in the Supplementary Online Material (SOM).

@@

The seismographic stations used in this study are plotted in Fig.~\ref{fig:eventsstations}(b) and
were selected to optimize global coverage
and high data quality.
In addition to the seismographic  stations used for the source inversions,
we included available data for our 1,480 event earthquake database from many data centers,
including IRIS, ORFEUS, INGV, IPGP, ETH, and GEONET.
Regional and temporary networks,
such as US Array~(TA),
Africa Array~(AF), the Canadian National Seismograph Network~(CN), Geoscience Australia~(AU),
the Antarctic Seismographic Argentinean Italian Network~(AI),
and the New Zealand National Seismograph Network~(NZ), \cyan{Japan?}
constitute a significant part
of our database and greatly improve coverage in certain regions.

@@

The misfit function to be minimized must
be carefully constructed.
In this study,
it involves cross-correlation traveltimes \citep[e.g.,][]{luo_wave-equation_1991}
for body waves and frequency-dependent multitaper phase measurements for surface waves \citep[e.g.,][]{laske_constraints_1996} \cyan{no multitaper measurements for body waves?}.
Measurements are made in several passbands of three-component seismograms rotated
into vertical, radial, and transverse components, resulting in a number of measurement
categories.
In this study, we consider four passbands, namely, a 17--40~s passband targeting body waves,
two 40--100~s passbands separately targeting body and surface waves,
and a 90--250~s passband targeting longer-period surface waves.
Each passband involves measurements on all three components,
which results in a total of twelve measurement categories.
Although the inversion is designed to minimize the overall misfit,
we track the misfit reduction in each of the categories to ensure that
the model is improving the fit to the data roughly equally.
One of the biggest challenges in the construction of the misfit function is the
highly uneven distribution of earthquakes and seismographic stations,
which must be counterbalanced by geographically weighting the data \citep[e.g.][]{Li1996}.
This issue is discussed in detail by~\cite{Ruanetal2018};
in this section we present a brief synopsis.

With these considerations in mind,
the overall misfit, $\Phi$, is defined as follows:
\begin{equation}
\label{eq:misfit}
\Phi = \sum_{s}^{S} \omega_s \sum_{c}^{C} \omega_{c} \sum_{r}^{R_{sc}} \omega_{scr} \sum_{w}^{W_{scr}} \omega_{scrw}\, \chi_{scrw}
\quad .
\end{equation}
Here~$S$ denotes the number of sources, $C$ the number of categories,
$R_{sc}$ the number of receivers recording source~$s$ in category~$c$,
and~$W_{scr}$ the number of measurement windows for source~$s$, category~$c$,
and receiver~$r$.
The misfit for a specific source~$s$, category~$c$, receiver~$r$, and window~$w$ is
\begin{equation}
  \chi_{scrw} = \frac{1}{\Delta\omega}\int_{\omega_1}^{\omega_2} \Big( \frac {\Delta \tau_{scrw}} {\sigma_{scrw}} \Big)^2\, \mathrm{d}\omega
\quad ,
\end{equation}
where~$\Delta \tau_{scrw}$ denotes a multi-taper frequency-dependent phase measurement over the frequency interval~$\Delta\omega=\omega_2-\omega_1$\,,
with associated uncertainties~$\sigma_{scrw}$\,.
For body waves, the window misfit is often simply the cross-correlation traveltime anomaly,
$\Delta T_{scrw}$\,, weighted by its standard deviation, i.e., $\chi_{scrw}=(\Delta T_{scrw}/\sigma_{scrw})^2$\,.
The window weights are all equal, $\omega_{scrw}=1$\,,
and the category weight, $\omega_c$\,, is the reciprocal of the number of measurements in that
category, $1/C$.
%Earthquakes mainly occur along plate boundaries, and most seismographic  stations are confined to the continents, which leads to an uneven distribution of sources and stations, as illustrated in Fig.~\ref{fig:eventsstations}. Therefore, weighting is crucial in global tomography to balance this uneven sampling of Earth's interior.
Our source and receiver weighting strategy,
encapsulated by the weights~$\omega_s$ and $\omega_{scr}$\,,
is developed to compensate for uneven spatial sampling.
We define source and receiver weights as
\begin{equation}
\omega_{s}^{-1} = N\,\sum_{s'=1}^{S} \exp\left[\mbox{}-\left(\frac{\Delta_{ss'}}{\Delta}\right)^2\right]
\quad ,
\label{eq:source_weights}
\end{equation}
and
\begin{equation}
\omega_{scr}^{-1} = N_{sc}\,\sum_{r'=1}^{R_{sc}} \exp\left[\mbox{}-\left(\frac{\Delta_{rr'}}{\Delta_{sc}}\right)^2\right]
\quad ,
\label{eq:receiver_weights}
\end{equation}
respectively.
Here~$N$ and~$N_{sc}$ are normalization factors,
and~$\Delta_{ss'}$ and~$\Delta_{rr'}$ denote angular distances between source and receiver pairs~$\{s,s'\}$ and~$\{r,r'\}$\,.
The reference angular distances~$\Delta$ and~$\Delta_{sc}$ need to be chosen based on the condition 
numbers of the diagonal weighting matrices defined by Eqns.~(\ref{eq:source_weights}) and~(\ref{eq:receiver_weights}).

@@

In this section we calculate specific changes in misfit using all 1,480
earthquakes and an identical set of weights and windows for three models,
namely, GLAD-M25, GLAD-M15, and S362ANI \citep{kustowski2008anisotropic} combined with CRUST2.0 \citep{bassin2000current} (S362ANI+CRUST2.0).
Table~\ref{table:misfit_reduction_M15_M25} summarizes the changes in fit in
the twelve measurement categories between the new model, GLAD-M25, and its
starting model, GLAD-M15, and between GLAD-M25 and model S362ANI+CRUST2.0, which was the starting model for the GLAD-M15 inversion.

@@

Another way to evaluate model quality is by assessing the distribution
of measurements in the various categories.
Again we use all 1,480 events and a set of identical windows on all three components
to assess GLAD-M25, GLAD-M15, and S362ANI+CRUST2.0.
The total number of selected windows,
determined using model GLAD-M25, exceeds 18~million.
Fig.~\ref{fig:phase_hist} shows histograms of the resulting phase
measurements in all twelve measurement categories.
We observe that the distributions generally become better centered on zero,
and that all standard deviations are steadily reduced.
The inversion is aimed at reducing the overall misfit,
so there are small tradeoffs between different measurement categories. \cyan{How were source corrections applied to GLAD-M15 and S362ANI+Crust2.0? Did you apply the correction terms computed for GLAD-M25 to all models?}

@@

Fig.~\ref{fig:psf_tests} shows the results of the four PSF tests we performed for model GLAD-M25.
The first test repeats an analysis performed by~\cite{bozdaug2016global} for GLAD-M15 in the upper mantle underneath Yellowstone.
That test was based on 253 earthquakes,
and Figs.~\ref{fig:psf_tests}a shows our result for the same location based on the current dataset of 1,480 events \cyan{Did you use all events in PSF tests or only a subset of them? I am asking just to confirm since I remember such a comment from Jeroen before}.
We observe that the 100~km diameter anomaly, which is smaller than that of used in GLAD-M15, at 300~km depth is well recovered, with little tradeoff between~$\beta_\mathrm{V}$ and~$\beta_\mathrm{H}$ and~$c$ (See SOM).
Figs.~\ref{fig:psf_tests}b--d shows the results of PSF tests for larger Gaussian anomalies (with 200~km to 400~km diameters) in the lower mantle beneath Afar,
in the lowermost mantle beneath Easter Island,
and in the mid mantle below Sumatra.
In each case the Gaussian anomaly is well recovered, with minimal tradeoff with other model parameters (See SOM).

@@

Following the approach of \cite{tape2009adjoint}, \cite{chen2015multiparameter},
and \cite{bozdaug2016global}, we selected 360 earthquakes that were not used
in the actual inversion. This held-out data set consists of magnitude 6.3--7.0
earthquakes in the global CMT catalog that were not used in the inversion.
We chose larger events to generate as many measurements as possible.
We calibrated the centroid time and scalar moment using a grid search based on
3D synthetics calculated in GLAD-M25.
Fig.~\ref{fig:events_360} summarizes the properties of the held-out database.

First, we repeated the misfit assessment discussed in
Section~\ref{section:Misfit assessment} for the held-out database.
Table~\ref{table:misfit_reduction_M15_M25_360} summarizes the reductions
in misfit for the held-out database for model GLAD-M25 compared to GLAD-M15
as well a S362ANI+CRUST2.0.
It is encouraging to see that the reductions are comparable to the
values tabulated in Table~\ref{table:misfit_reduction_M15_M25} for the actual inversion.
Overall, the reductions are slightly smaller, partly due to the fact that we did not
conduct full CMT inversions for the held-out database \cyan{not sure..}.

\begin{table}
  \centering
  %\label{tab:category}
  \begin{tabular}{|c|c|c|c|}
  \hline
  ~          &  Vertical (\%) & Radial (\%) &  Transverse (\%) \\
  \hline
  17--40~s                &          11.8 (29.2) &       14.1 (33.7) &       21.5 (43.4) \\
  40--100~s body waves    &          14.5 (26.2) &       12.9 (32.2)  &       16.9 (39.0) \\
  40--100~s surface waves &          29.3 (49.1) &       28.1 (49.4) &       23.7 (51.2) \\
  90--250~s               &          10.9 (30.9) &       14.3 (34.8)  &       24.0 (34.9) \\
  \hline
  \end{tabular}\\
  \caption{\small{Changes in fit for 360 earthquakes not used in the inversion in the twelve measurement categories
between the new model, GLAD-M25, and its starting model, GLAD-M15, and, in parentheses, between GLAD-M25 and model S362ANI+CRUST2.0, which was the starting model for the GLAD-M15 inversion.}}
  \label{table:misfit_reduction_M15_M25_360}
\end{table}

@@

Vertical cross sections are plotted relative to the spherical average of GLAD-M25,
as discussed in Appendix~\ref{sec:1Dmodel}.
For plotting purposes and use in other applications,
an expansion of the model in spherical harmonics and radial B-splines is
discussed in Appendix~\ref{sec:shanalysis} \cyan{but the models were not expanded to spherics harmonics to plot in this paper, right?}.

@@

Relative to our first generation model GLAD-M15,
we observe a significant increase in model perturbation amplitudes and resolution,
both in the upper and lower mantle.
To illustrate this point,
Fig.~\ref{fig:power} and Fig.~\ref{fig:powerspectraradius} show normalized power per angular degree (Eqn.~\ref{eq:powerdegree}) and normalized power per angular degree as a function of radius (Eqn.~\ref{eq:powerdegreeradius}), respectively, for models S362ANI, GLAD-M15, and GLAD-M25.
Model S362ANI has no power beyond degree~18,
and we see an increase in power for GLAD-M25 relative to GLAD-M15 beyond degree~10 throughout the mantle.

@@

As illustrated in Fig.~\ref{fig:M25-AFAR},
we see an enhancement of the Afar plume relative to GLAD-M15.
The 3D morphology of the African superplume shows a mantle plume rising from the core-mantle boundary with a broad base tilting northward \cyan{do you know why the African plume tilts? I think Pacific plume tilts likely because of the plate motion. GLAD-M25 generally shows that this tilt is happening widely in the upper mantle and perhaps the top of the lower mantle. But the African plume's tilt start from the CMB} with a thinning neck, before it reaches the 660~km phase boundary and flattens.
It then develops into two sub-plumes ---Afar and East Lake Victoria--- supplying the East Africa rift.
The development of the superplume and its 3D morphology might be associated with water in the mantle transition zone, a possibility we will explore in a future study.

Subduction along the Andes in South America is imaged from south to north all the way down to the transition zone and beyond in a more continuous way compared to GLAD-M15, as shown in Fig.~\ref{fig:S_America}.
In the contour plot of positive shear-wavespeed perturbations we observe three gaps, which may correspond to ridges or volcanic plateaus on the subducted Nazca plate, and indicate a weakened or even torn slab \cyan{I think it is a great story but would you like to put the contour plot here or reserve for the future paper?}.

Fig.~\ref{fig:M24-Iceland} showcases the north Atlantic, where we see clear expressions of the Jan Mayen and Iceland plumes as well as the Azores, Canary Islands, and Bermuda,
and Fig.~\ref{fig:M24-Reunion} shows the emergence of hotspots in the Indian Ocean in model GLAD-M25,
including Marion, Crozet, Kerguelen, Cocos, R\'eunion, and Seychelles.The visual inspection of the models show significant increase in perturbation anomalies in GLAD-M25 compared to GLAD-M15 that explains the misfit reductions in histograms (Figs.~\ref{fig:phase_hist}~\&~\ref{fig:phase_hist_360}).

@@

Overall, the three models are in reasonably good agreement.
At shallow depths, model GLAD-M25 shows more distinct continental crust and cratons, thanks to the inclusion of surface waves.
But in the upper and mid mantle,
the models share similar attributes. Relatively smoother slabs in GLAD-M25 are likely related to our choice of smoothing considering the minimum period of body waves in our simulations, $\sim17$~s, which is longer than typical teleseismic body-wave tomography studies.

@@

Although Figs.~\ref{fig:window_density_Z}--\ref{fig:window_density_T} illustrate that much information in seismograms is
being assimilated, we still have a long way to go before explaining every broadband wiggle in hundreds-of-minutes-long seismograms.
Currently, we are only fitting the phase in selected time windows, and amplitude information remains completely unused.
We accommodate the full physics of seismic wave propagation,
but we are not exploiting the most general earth model parameterization.
GLAD-M25 is an elastic model with radial anisotropy confined to the upper mantle similar to its precessor GLAD-M15.
It is well known that the upper mantle is azimuthally anisotropic~\citep[e.g.,][]{montagner1989petrological,montagner1991},
and we also know that amplitude information helps constrain second derivatives in phase speed~\citep[e.g.,][]{WW86,TDI,TDII},
in addition to lateral variations in attenuation~\cite[e.g.,][]{romanowicz1998,reidetal2001,DaEkDz08}.
Thus, the natural next step in global FWI is to use phase and amplitude information simultaneously to jointly constrain the elastic and anelastic structure of the Earth.
To accomplish this next step, source parameters need to be constrained more precisely, especially as we push the resolution to shorter periods~\citep[e.g.,][]{valentine2010}.
